Analysing the Performance of Shallow-Water Models with the Roofline Model

### 2017-01-24 docs/papers/roofline_habakkuk/habakkuk.tex
habakkuk paper: tweak text and add mulsd/divsd overlap data file

Obtaining a performance estimate by simply counting all of the FLOPs
that must be performed is equivalent to assuming that they are all
executed sequentially. However, a core a current CPU is likely to have
support for Instruction Level Parallelism.

@@

So far we have considered only single-core performance. In reality,
any application seeking to achieve good performance will run in
parallel on multiple CPU cores.  If we restrict ourselves to running a
single process/thread per core then clearly that thread will have
exclusive use of that core's registers and execution units. Resources
shared between cores such as L2 cache or bandwidth to main memory will
however be shared by the executing threads.

>>>>

Obtaining a performance estimate by simply counting all of the FLOPs
that must be performed is equivalent to assuming that they are all
executed sequentially. However, a core on any recent generation of CPU
is likely to have support for Instruction Level Parallelism.

@@

So far we have considered only single-core performance. In reality,
any application seeking to achieve good performance will run in
parallel on multiple CPU cores.  If we restrict ourselves to running a
single process/thread per core then clearly that thread will have
exclusive use of that core's registers and execution units. Resources
shared between cores (such as L2 cache or bandwidth to main memory) will
however be shared by the executing threads.
